---
title: "FPL Project"
author: "Fungai Jani"
date: '2022-11-02'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ISLR)
library(tidyverse)
library(Stat2Data)
library(mosaic)
library(ggplot2)

library(readr)
fpl <- read_csv("FPL 20 21.csv")
```

```{r}
##Players that play 0 minutes will have 0 points so it is best we remove these players and only considers players that have played
fpl<-fpl[!(fpl$Minutes==0 ),]
fpl

fplcor <- select(fpl, Total_Points, Minutes, Goals_Scored, BPS, Yellow_Cards, Influence)
```

##Number statistics for the response variable and the possible predictor variables
```{r}
favstats(fpl$Total_Points)
```

```{r}
favstats(fpl$Influence)
```

```{r}
favstats(fpl$ICT_Index)
```

```{r}
favstats(fpl$Minutes)
```


```{r}
favstats(fpl$BPS)
```

```{r}
favstats(fpl$Goals_Scored)
```


```{r}
favstats(fpl$Assists)
```

```{r}
favstats(fpl$Yellow_Cards)
```


```{r}
##Histogram to see the distribution of the points scored in the dataset 
gf_histogram(~Total_Points, data = fpl) + ggtitle("Distribution of Total Points")+ xlab("Total Points")+
  ylab("Count")+
  labs(caption = "Data used to create this scatterplot was taken from kaggle.com", subtitle = "FPL 2020/2021 Season")
```
#Checking the relationship between predictor and response variables using scatterplots

```{r}

ggplot(data = fpl, aes(x = Influence, y= Total_Points)) + geom_point(shape = 23) + ggtitle("Relationship between Influence and Total Points")+ xlab("Influence")+
  ylab("Total Points")+
  labs(caption = "Data used to create this scatterplot was taken from kaggle.com", subtitle = "FPL 2020/2021 Season")
```

```{r}
gf_point(Total_Points~ ICT_Index, data=fpl)
```


```{r}
gf_point(Total_Points~ Goals_Scored, data=fpl)
```

```{r}
gf_point(Total_Points~ Minutes, data=fpl)
```


##I decided to see the total points scored by each position, to  see which position produces the most fantasy points.

```{r}
FPL = fpl %>% group_by(Position)  %>% summarise(total_points =mean(Total_Points), influence = mean(Influence))
FPL
```
##Seeing correlation between different variables such as minutes and goals scored for an interaction term
```{r}

cor.test(Minutes ~ Goals_Scored, data = fpl)
```

```{r}
cor.test(Minutes ~ Assists, data = fpl)
```

```{r}
cor.test(Minutes ~ Influence, data = fpl)
#high correlation between minutes and influence
```
```{r}
cor.test(Total_Points ~ Influence, data = fpl)
```
```{r}
fpl1.lm <- lm(Total_Points~ Influence + Minutes + Goals_Scored,  data = fpl)
summary(fpl1.lm)
```

```{r}
anova(fpl1.lm)
```

```{r}
fpl2.lm <- lm(Total_Points~ Influence + Minutes + Goals_Scored * Assists + BPS,  data = fpl)
summary(fpl2.lm)
```

```{r}
fpl3.lm <- lm(Total_Points~ Minutes + Goals_Scored + Assists + BPS,  data = fpl)
summary(fpl3.lm)
```
```{r}
fpl4.lm <- lm(Total_Points~ Influence*Minutes + Goals_Scored + Assists + BPS + Yellow_Cards,  data = fpl)
summary(fpl4.lm)
```
```{r}
fpl5.lm <- lm(Total_Points~ Influence + Minutes + Goals_Scored + Assists + BPS + Yellow_Cards + Influence*Position,  data = fpl)
summary(fpl5.lm)
```

```{r}
confint(fpl5.lm, level=.95)
```

```{r}
cor(fplcor)
```

```{r}
anova(fpl5.lm)
```

```{r}
cor.test(Total_Points ~ Yellow_Cards, data = fpl)
```

```{r}
plot(fpl5.lm)
```

